Preventing runtime errors of Redis at compile time

### 2015-11-19 paper.tex
8. Discussions

\begin{minted}[xleftmargin=1em]{haskell}
del :: KnownSymbol s
    => Proxy s
    -> Edis xs (Del xs s) (Either Reply Integer)
del key = Edis $ Hedis.del (symbolVal key)
\end{minted}

\mintinline{haskell}{KnownSymbol} is a class that gives the string associated
 with a concrete type-level symbol, which can be retrieved with
 \mintinline{haskell}{symbolVal}.\footnotemark

\footnotetext{They are defined in \mintinline{haskell}{GHC.TypeLits}.}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
set :: KnownSymbol s
    => Proxy s
    -> ByteString       -- data to store
    -> Edis xs (Set xs s Strings) (Either Reply Status)
set key val = Edis $ Hedis.set (symbolVal key) val
\end{minted}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
set :: (KnownSymbol s, Serialize x)
    => Proxy s
    -> x       -- can be anything, as long as it's serializable
    -> Edis xs (Set xs s (StringOf x)) (Either Reply Status)
set key val = Edis $ Hedis.set (symbolVal key) (encode val)
\end{minted}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
incr :: (KnownSymbol s, Get xs s ~ Just (StringOf Integer))
     => Proxy s -> Edis xs xs (Either Reply Integer)
incr key = Edis $ Hedis.incr (symbolVal key)

incrbyfloat :: (KnownSymbol s, Get xs s ~ Just (StringOf Double))
     => Proxy s -> Double -> Edis xs xs (Either Reply Double)
incrbyfloat key n = Edis $ Hedis.incrbyfloat (symbolVal key) n
\end{minted}

@@

\begin{minted}[xleftmargin=1em]{haskell}
llen :: (KnownSymbol s, Get xs s ~ Just (ListOf x))
        => Proxy s
        -> Edis xs xs (Either Reply Integer)
llen key = Edis $ Hedis.llen (symbolVal key)
\end{minted}

@@

As many other list-related commands also have this "List or Nothing" semantics,
 we could abstract the lengthy type constraint above and give it an alias with
 type synonym.

@@

\begin{minted}[xleftmargin=1em]{haskell}
llen :: (KnownSymbol s, ListOrNX xs s)
        => Proxy s
        -> Edis xs xs (Either Reply Integer)
llen key = Edis $ Hedis.llen (symbolVal key)
\end{minted}

@@

\section{Discussions}
\paragraph{Syntax}
\paragraph{Commands with multiple inputs or outputs}
\paragraph{Redis Transactions}
\section{Conclusion and Related Work}
\paragraph{Acknowledgements}

>>>>

\begin{minted}[xleftmargin=1em]{haskell}
del :: KnownSymbol s
    => Proxy s
    -> Edis xs (Del xs s) (Either Reply Integer)
del key = Edis $ Hedis.del (encodeKey key)
\end{minted}

\mintinline{haskell}{KnownSymbol} is a class that gives the string associated
 with a concrete type-level symbol, which can be retrieved with
 \mintinline{haskell}{symbolVal}.\footnotemark
 Where \mintinline{haskell}{encodeKey} converts \mintinline{haskell}{Proxy s} to
 \mintinline{haskell}{ByteString}.
\footnotetext{They are defined in \mintinline{haskell}{GHC.TypeLits}.}

\begin{minted}[xleftmargin=1em]{haskell}
encodeKey :: KnownSymbol s => Proxy s -> ByteString
encodeKey = encode . symbolVal
\end{minted}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
set :: KnownSymbol s
    => Proxy s
    -> ByteString       -- data to store
    -> Edis xs (Set xs s Strings) (Either Reply Status)
set key val = Edis $ Hedis.set (encodeKey key) val
\end{minted}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
set :: (KnownSymbol s, Serialize x)
    => Proxy s
    -> x       -- can be anything, as long as it's serializable
    -> Edis xs (Set xs s (StringOf x)) (Either Reply Status)
set key val = Edis $ Hedis.set (encodeKey key) (encode val)
\end{minted}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
incr :: (KnownSymbol s, Get xs s ~ Just (StringOf Integer))
     => Proxy s -> Edis xs xs (Either Reply Integer)
incr key = Edis $ Hedis.incr (encodeKey key)

incrbyfloat :: (KnownSymbol s, Get xs s ~ Just (StringOf Double))
     => Proxy s -> Double -> Edis xs xs (Either Reply Double)
incrbyfloat key n = Edis $ Hedis.incrbyfloat (encodeKey key) n
\end{minted}

@@

\begin{minted}[xleftmargin=1em]{haskell}
llen :: (KnownSymbol s, Get xs s ~ Just (ListOf x))
        => Proxy s
        -> Edis xs xs (Either Reply Integer)
llen key = Edis $ Hedis.llen (encodeKey key)
\end{minted}

@@

As many other list-related commands also have this "List or nothing" semantics,
 we could abstract the lengthy type constraint above and give it an alias with
 type synonym.

@@

\begin{minted}[xleftmargin=1em]{haskell}
llen :: (KnownSymbol s, ListOrNX xs s)
        => Proxy s
        -> Edis xs xs (Either Reply Integer)
llen key = Edis $ Hedis.llen (encodeKey key)
\end{minted}

@@

\section{Discussions}
\paragraph{Syntax}
No one could ignore the glaring shortcoming of the syntax, which occurs mainly
 in two places: symbol singletons and indexed monad. We are hoping that these
 issues could be solved with future syntactic extensions.

\paragraph{Returns only determined datatypes}

All other data structures in Redis also follow the semantics similar to
 "List or nothing" as \mintinline{text}{LLEN} has. Take the case of
 \mintinline{text}{GET}, which has a similar semantics that should be typed:

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
get :: (KnownSymbol s, Serialize x, StringOrNX xs s)
    => Proxy s -> Edis xs xs (Either Reply (Maybe x))
\end{minted}

Since the key may not exist, we don't know what \mintinline{haskell}{x} would
be. We could left \mintinline{haskell}{x} ambiguous, and let it be decided by
 the caller. But users will then be forced to spell out the complete
type signature of everything, including the dictionaries, only to specify
the desired resulting type.

Instead of allowing the key to be non-existent, we require that the key must
 exist and it's associating type to be determined at compile time. So our
 version of \mintinline{haskell}{get} has a stricter semantics:

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
get :: (KnownSymbol s, Serialize x
     , Just (StringOf x) ~ Get xs s)
    => Proxy s -> Edis xs xs (Either Reply (Maybe x))
\end{minted}

\paragraph{Commands with multiple inputs or outputs}

Some command may take a variable number of arguments as inputs, and returns more
 than one value as outputs. To illustrate this, consider
 \mintinline{haskell}{sinter} in \mintinline{haskell}{Hedis}:

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
Hedis.sinter :: [ByteString]                      -- keys
             -> Redis (Either Reply [ByteString]) -- values
\end{minted}

In Hedis such command could easily be expressed with lists of
 \mintinline{haskell}{ByteString}s. But in Edis, things escalate quickly, as
 the keys and values will have to be expressed with heterogeneous
 lists\cite{hetero}, which would be pratically infeasible, considering the cost,
 if not impossible.

Most importantly, the keys will all have to be constrained by
 \mintinline{haskell}{KnownSymbol}, which enforces these type literals to be
 concrete and known at compile time.
 It's still unclear whether this is possible.

So instead, we are offering commands that only has a single input and output.

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
sinter :: ByteString                      -- single key
       -> Redis (Either Reply ByteString) -- single value
\end{minted}

\paragraph{Redis Transactions}

\section{Conclusion and Related Work}
\paragraph{Acknowledgements}
